### 2016-03-10 chapters/background.tex

\subsection{Feature Models}
Feature models are multi-purpose tool for product lines. Figure~\ref{img-fm} shows a simplified example of a feature model.
\begin{figure}
	\includegraphics{img/img-fm.png}
	\caption{A simple example of a feature model}
	\label{img-fm}
\end{figure}
Amongst their benefits are:
\begin{itemize}
\item Visualization of the possible features and their hierarchy
\item Classification of features and their dependencies (alternative/or; optional/mandatory/abstract)
\item Formal Representation of the whole product line $\Rightarrow$ computationally processable
\item Assistance/foundation for configuration and variant validation
\end{itemize}
They are basically structured like trees: There is a root node, an arbitrary number of levels of nodes and finally leaf nodes without child nodes of their own. In that manner feature models map the hierarchy of features. In addition they mark each feature as either mandatory or optional as well as either abstract or concrete. The possible relationships of multiple features with a mutual parent feature are \textit{or} (at least one feature has to be selected), \textit{alternative} (exactly one feature has to be selected) and \textit{and} (any number of features can be selected). As features' relations may be of higher complexity than just parent-child relations additional constraints can be noted within a feature model. Constraints are boolean expressions, the example in figure~\ref{img-fm} shows an implication.

>>>>

\subsection{Feature Models}
Feature models are multi-purpose tool for product lines. Figure~\ref{img-fm} shows a simplified example of a feature model.
\begin{figure}
	\includegraphics{img/img-fm.png}
	\caption{A simple example of a feature model}
	\label{img-fm}
\end{figure}
Amongst their benefits are:
\begin{itemize}
\item Visualization of the possible features and their hierarchy
\item Classification of features and their dependencies (alternative/or; optional/mandatory/abstract)
\item Formal Representation of the whole product line $\Rightarrow$ computationally processable
\item Assistance/foundation for configuration and variant validation
\end{itemize}
They are basically structured like trees: There is a root node, an arbitrary number of levels of nodes and finally leaf nodes without child nodes of their own. In that manner feature models map the hierarchy of features. In addition they mark each feature as either mandatory or optional as well as either abstract or concrete. The possible relationships of multiple features with a mutual parent feature are \textit{OR} (at least one feature has to be selected), \textit{ALTERNATIVE} (exactly one feature has to be selected) and \textit{AND} (any number of features can be selected). As features' relations may be of higher complexity than just parent-child relations additional constraints can be noted within a feature model. Constraints are boolean expressions, the example in figure~\ref{img-fm} shows an implication.
